Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
ok

  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
     geom_line(aes(linetype = publication_place)) +
     geom_point(aes(shape = publication_place), size = 3) +
     #scale_y_log10() +
     #facet_wrap(catalog ~ .) + 
     ylab("Title count (n)") + xlab("Publication year") +  
     ggtitle(catal)
  print(p)

>>>>

  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
     geom_line(aes(linetype = publication_place)) +
     geom_point(aes(shape = publication_place), size = 3) +
     ylab("Title count (n)") + xlab("Publication year") +  
     ggtitle(catal)
  print(p)
